Reviving the Lost Art of \\Combinator Graph Reduction

### 2023-01-30 experiments/superg/doc/paper/paper.tex
Start bracket abstraction.

%Starting from a lambda calculus expression, we first translate it into an expression consisting exclusively of the application of a small set of predefined functions, or \textit{combinators}.
%It turns out that any lambda calculus expression can be expressed using just three combinators:
%\begin{itemize}
%    \item $S \ f \ g \ x = f \ x \ (g \ x)$
%    \item $K \ x \ y = x$
%    \item $I \ x = x$\footnote{It turns out that $SKK = I$, so even this combinator is not strictly necessary, but all reasonable implementations do include $I$, and it simplifies the example.}
%\end{itemize}
%
%For example, $\lambda x.x+1$ can be converted into the combinator expression:
%
%\[
%    S \ (S \  (K \  +) \  I) \ (K \ 1)
%\]
%
%We invite the reader to verify this by applying $x$ to this expression and reducing it to $x+1$ with the usual $\beta$-reduction rule.
%While the generated expression is not as easy to read, the simplicity of its components is appealing: to execute a program compiled to combinators, an evaluator only needs to support four operations: the built-in $S$, $K$ and $I$ combinators, and function application\footnote{And any builtins of the language, like the plus operator in the example.}.
%Better still, conversion to combinators removes all bound variables.
%The runtime need not concern itself with passing arguments, this is all handled by the combinators.
%
%\textbf{TODO: } Combinators $B$ and $C$.
%
\subsection{Bracket Abstraction}

>>>>

%Starting from a lambda calculus expression, we first translate it into an expression consisting exclusively of the application of a small set of predefined functions, or \textit{combinators}.
%It turns out that any lambda calculus expression can be expressed using just three combinators:
%\begin{itemize}
%    \item $S \ f \ g \ x = f \ x \ (g \ x)$
%    \item $K \ x \ y = x$
%    \item $I \ x = x$\footnote{It turns out that $SKK = I$, so even this combinator is not strictly necessary, but all reasonable implementations do include $I$, and it simplifies the example.}
%\end{itemize}
%
%For example, $\lambda x.x+1$ can be converted into the combinator expression:
%
%\[
%    S \ (S \  (K \  +) \  I) \ (K \ 1)
%\]
%
%We invite the reader to verify this by applying $x$ to this expression and reducing it to $x+1$ with the usual $\beta$-reduction rule.
%While the generated expression is not as easy to read, the simplicity of its components is appealing: to execute a program compiled to combinators, an evaluator only needs to support four operations: the built-in $S$, $K$ and $I$ combinators, and function application\footnote{And any builtins of the language, like the plus operator in the example.}.
%Better still, conversion to combinators removes all bound variables.
%The runtime need not concern itself with passing arguments, this is all handled by the combinators.
%
%\textbf{TODO: } Combinators $B$ and $C$.
%
\subsection{Bracket Abstraction}
Bracket Abstraction is the traditional algorithm for compiling lambda calculus expressions into combinatory logic.
The basic algorithm requires only the $S$, $K$, and $I$ combinators.
Its compilation function can be defined recursively as:

\begin{equation*}
    \begin{array}{l l l}
        C [[\ e_1\ e_2\ ]]     & = & C [[\ e_1\ ]]\ C [[\ e_2\ ]]                  \\
        C [[\ \lambda x.e\ ]]  & = & A\ x\ [[\ C [[\ e\ ]]\ ]]                     \\
        C [[\ cv\ ]]           & = & cv                                            \\
        \\
        A\ x\ [[\ f_1\ f_2\ ]] & = & \ S\ (A\ x\ [[\ f_1\ ]])\ (A\ x\ [[\ f_2\ ]]) \\
        A\ x\ [[\ x\ ]]        & = & I                                             \\
        A\ x\ [[\ cv\ ]]       & = & K\ cv                                         \\
    \end{array}
\end{equation*}

Any lambda calculus expression can be compiled using this algorithm.

TODO more!
